--- 
#yaml#
title:    "Latex Snips Handbook"
author:   "to-ohru iwanami {the hatch keeper}"
date: |   
      | \vhCurrentDate
      | version \vhCurrentVersion
      | InsightHatch: "LatexSnips"
      | \textbf{IH-LatexSnips-v}\textbf{\vhCurrentVersion}
documentclass:    book
output:
  pdf_document:
    latex_engine:       lualatex
    toc:                yes
    number_sections:    yes
    keep_tex:           yes
    fig_caption:        yes
subtitle: \textit{Insight Hatch Machine Leanring Reviews - Vol 2}
#bibliography: citations.bib
#csl: microbiology.csl
link-citations:         yes
nocite: '@*'
fontsize:               12 pt
geometry:               margin = 0.9in
linestretch:            1.25
papersize:              a4

#latex header
header-includes:
 - |
  ```{=latex}
  \usepackage{pgfplots}
  \newcommand{\docTitle}{Latex Snips Dictionary}

  \raggedbottom                         % ensures no page fill

  % setup special chapter only counter
  \newcounter{chonlycounter}
  \renewcommand{\thechonlycounter}{\thechapter}

  % setup some special branding fonts 
  % (this is only used at start of document - for product names )
    \usepackage{fontspec}
    \usepackage{textcomp}
    \newfontface\poppins{Poppins}[Path=fonts/, 
                              UprightFont=*-Regular, 
                              BoldFont=*-Bold]
    \newcommand{\textpoppins}[1]{{\poppins #1}}
  
    \newfontface\fluxreg{FluxRegular}[Path=fonts/, 
                              UprightFont=*.otf]
    \newcommand{\textfluxreg}[1]{{\fluxreg #1}}
  
    \newfontface\lato{Lato}[Path=fonts/, 
                              UprightFont=*-Regular]
    \newcommand{\textlato}[1]{{\lato #1}}
  
    \newfontface\ssp{SourceSansPro}[Path=fonts/, 
                              UprightFont=*-Regular]
    \newcommand{\textssp}[1]{{\ssp #1}}
  
    \newfontface\couriernew{Courier New}
    \newcommand{\textcouriernew}[1]{{\couriernew #1}}
  
    \newfontface\arial{Arial}
    \newcommand{\textarial}[1]{{\arial #1}}
  
    \newfontface\palatino{Palatino}
    \newcommand{\textpalatino}[1]{{\palatino #1}}

  % FOR GRAPHICS tikz and pgfplots
  \usepackage{pgfplots}                % math plotting
  \pgfplotsset{compat=1.18}

  \usepackage{rotating}
  
  \usepackage{hyperref}
  \usepackage{cleveref}

  \usepackage{tikz}                    % tikz megatool
  \usepackage{tikz-3dplot}
  \usetikzlibrary{arrows.meta,shapes,backgrounds}

  %\usepackage{fvextra}                 % special linebreaking 
  %\DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
  
  %\usepackage[skins]{tcolorbox}
  \usepackage{listings}
  \usepackage{booktabs}
  \usepackage{changepage}               % width formatting on page

  \definecolor{dblu}{HTML}{002db3}
  %\definecolor{cyan}{HTML}{99ccff}
  %\definecolor{ltorng}{HTML}{99ccff}
  %\definecolor{ltgrn}{HTML}{002db3}

  \usepackage{titling}
 
  % testing 20240414 - margin methods - to adjust
  
  \usepackage{layout}       % for margins setting ->employ:"\layout"
  \usepackage{multicol}  
  \usepackage{geometry} 

  % Set asymmetric page margins (book formatting)
  \geometry{
  inner=0.75in,   % Inner margin
  outer=1.0in,    % Outer margin
  bottom=0.6in,   % Bottom margin
  top=0.6in,      % Bottom margin
  includeheadfoot  }

  %\usepackage{lipsum}         % Generates filler text
  
  % math fonts and coloring
  \usepackage{amsmath}
  \usepackage{amsthm}
  \usepackage{amssymb}        % specific symbols
  \usepackage{mathrsfs}
  \usepackage{xcolor}         % For coloring text
  \usepackage{graphicx}

  \definecolor{impactblue}{RGB}{30, 144, 255}
  \definecolor{royalimpactblue}{RGB}{65, 105, 225} % Royal Blue, more vivid
  \definecolor{navyimpactblue}{RGB}{0, 0, 128} %  avy Blue tone 
   
  \usepackage{caption}
  \usepackage{subcaption}
  \usepackage{adjustbox}
  \usepackage{float}
  
  % so that weblinks are colored bluw
  \usepackage{hyperref}
  \hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
  }
  
  
  \usepackage{enumitem}
  \usepackage{varwidth}
  \usepackage[nochapter, tocentry, owncaptions, tablegrid]{vhistory}
  \usepackage{tasks}
  \usepackage{scrlayer-scrpage}
  \numberwithin{equation}{section}
  \usepackage{lastpage}
  \captionsetup[figure]{font=small,labelfont=small}

  % Regular Theorems, definitions, lemmas, proofs
  
  \theoremstyle{plain}      % from `amsthm'
  \newtheorem{theorem}{Theorem}
 
  \theoremstyle{definition} % from `amsthm'
  \newtheorem{defn}{Definition}
  
  \newtheorem{xmpl}{Example}% from `amsthm'
  
  \theoremstyle{remark}     % from `amsthm'
  \newtheorem{remark}{Remark}
  
  \newtheorem{algorithm}{Algorithm} 
  \newtheoremstyle{note}    % style name
  {2ex}                     % above space
  {2ex}                     % below space
  {}                        % body font
  {}                        % indent amount
  {\scshape}                % head font
  {.}                       % post head punctuation
  {\newline}                % post head punctuation
  {}                        % head spec
  
  \theoremstyle{note}         % from `amsthm'
  \newtheorem{scnote}{Note}  

  % Colorbox - Theorems, definitions, lemmas, proofs

  \usepackage[most]{tcolorbox}          % does not included 'minted' (issue with rmd) 
  \newtheorem{lem}{Lemma}		% from `amsthm'
  \newtheorem{pruf}{Proof}		% from `amsthm'

  \newtcbtheorem[number within=chapter]{a_thm}{Theorem}
  {enhanced,frame empty,interior empty,colframe=green!50!white,
    coltitle=green!40!black,fonttitle=\bfseries,colbacktitle=green!15!white,
    borderline={0.5mm}{0mm}{green!15!white},  
    attach boxed title to top left={yshift=-2mm},
    boxed title style={boxrule=0.4pt},varwidth boxed title, , 
    breakable, colback=white
  }{theo}

  % This is for Key Equations - and only indexes the Charter Number
  % Should use only once in a Chapter 
  \newtcbtheorem[use counter=chonlycounter]{a_def_eq}{Key ML Equation}
  {enhanced,frame empty,interior empty,colframe=blue!50!white,
    coltitle=blue!40!black,fonttitle=\bfseries,colbacktitle=blue!15!white,
    borderline={0.5mm}{0mm}{blue!15!white},
    attach boxed title to top left={yshift=-2mm},
    boxed title style={boxrule=0.4pt},varwidth boxed title, 
    breakable, colback=white
  }{def_eq}

  \newtcbtheorem[number within=chapter]{a_def}{Definition}
  {enhanced,frame empty,interior empty,colframe=blue!50!white,
    coltitle=blue!40!black,fonttitle=\bfseries,colbacktitle=blue!15!white,
    borderline={0.5mm}{0mm}{blue!15!white},
    attach boxed title to top left={yshift=-2mm},
    boxed title style={boxrule=0.4pt},varwidth boxed title, 
    breakable, colback=white
  }{defi}

  \newtcbtheorem[number within=chapter]{a_exmp}{Example}
  {enhanced,frame empty,interior empty,colframe=cyan!50!white,
    coltitle=cyan!20!black,fonttitle=\bfseries,colbacktitle=cyan!15!white,
    borderline={0.5mm}{0mm}{cyan!15!white},
    attach boxed title to top left={yshift=-2mm},
    boxed title style={boxrule=0.4pt},varwidth boxed title, , 
    breakable, colback=white
  }{exmp}
  
  \newtcbtheorem[number within=chapter]{a_lemma}{Lemma}
  {enhanced,frame empty,interior empty,colframe=cyan!50!white,
    coltitle=cyan!20!black,fonttitle=\bfseries,colbacktitle=cyan!15!white,
    borderline={0.5mm}{0mm}{cyan!15!white},
    attach boxed title to top left={yshift=-2mm},
    boxed title style={boxrule=0.4pt},varwidth boxed title, , 
    breakable, colback=white
  }{lema}

  \tcolorboxenvironment{lem}{
  enhanced jigsaw,colframe=cyan,interior hidden, breakable,before skip=10pt,after skip=10pt 
  }
  \tcolorboxenvironment{pruf}{			
  blanker,breakable,left=5mm,
  before skip=10pt,after skip=10pt,
  borderline west={1mm}{0pt}{red}
  }

  \pretitle{%
  \begin{flushleft} \LARGE
  \includegraphics[width=2cm,height=2cm]{pictures/IH2.jpg}
  \end{flushleft}
  \begin{flushright} \LARGE
  }
  
  \posttitle{\end{flushright}}
  \preauthor{\begin{flushright}}
  \postauthor{\end{flushright}}
  \predate{\begin{flushright}}
  \postdate{\end{flushright}}
  
  \ohead[]{IH - Machine Learning Reviews}
  \ifoot{\hsize=350pt \docTitle\ -- Version \vhCurrentVersion}
  \ofoot{\thepage~/~\pageref{LastPage}}
  \cfoot[]{}
  ```

---
<!-- headers above -->
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  fig.pos = 'h',
  tidy.opts = list(width.cutoff = 60),
  fig.width = 4, 
  fig.height = 3, 
  fig.cap = "Default caption for all figures",  # Optional default caption
  fig.align = "center"
)
library(reticulate)           # Python integration
# cat("\\small\n")
```

\begin{versionhistory}
  \vhEntry{0.00.0}{2024.11.11}{DP}{Created!}
\end{versionhistory}
\newpage

\setcounter{table}{0}


\frontmatter
# Prefice and Introduction



\newpage

# r markdown code block tricks

In this example, the backticks are used to encapsulate the LaTeX code, and it will be displayed as plain text in the output.

## LaTeX Code Block that Renders

To create a LaTeX code block that renders and displays the content as formatted output, you can use the same syntax but without the outer backticks. Instead, you simply write:



#### Formula inline double dollar sign
$$
x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
$$


## LaTeX Code Block Example

To display the quadratic formula as a block equation, use the following syntax:

```{r, echo=FALSE}
# This chunk is used for any R code if needed
2;
```


\newpage

# tikzs

\newpage

## frist pic

\begin{tikzpicture}
  \def\xmin{0}
  \def\xmax{10}
  \def\ymin{0}
  \def\ymax{10}
  \draw[style=help lines, ystep=1, xstep=1] (\xmin,\ymin) grid
  (\xmax,\ymax);

  \draw (-.25,-.25) node[auto] {0};
  \draw[->] (\xmin,\ymin) -- (\xmax,\ymin) node[right] {$Q$};
  \draw[->] (\xmin,\ymin) -- (\xmin,\ymax) node[above] {$P$};

  \def\intersectX{4.76}
  \def\intersectY{4.26}
  \def\QPX{4}
  \def\QPY{5}
  \draw[color=red] plot [domain=0:8] (\x,{((\x)^2)/10 +2)});
  \draw[color=blue] plot [domain=0:8] (\x,{((\x-14)^2)/20)});

  \fill[fill=pink,opacity=0.7] (0,\QPY) -- plot [domain=0:\QPY] (\x,{((\x-14)^2)/20)}) -- (\QPX,\QPY) -- cycle;
  \fill[fill=cyan,opacity=0.7] (0,\QPY) -- plot [domain=0:\QPX] (\x,{((\x)^2)/10 +2)}) -- (\QPX,\QPY) -- cycle;

  \draw [domain=\QPX:\intersectX]  plot(\x,{((\x-14)^2)/20)}) -- (\QPX,\QPY) -- (\QPX,\QPY) -- cycle; 

  \draw [fill=green,opacity=0.7,domain=\QPX:\intersectX]  plot(\x,{((\x)^2)/10 +2)}) -- (\QPX,\QPY) -- cycle;

  \draw[dashed]  (\intersectX,0) node[below] {$Q_1$} -- (\intersectX,\intersectY);
  \draw[dashed]  (0,\intersectY) node[below] {$P_1$} -- (\intersectX,\intersectY);
  \draw[dashed]  (0,\intersectY) node[below] {$P_1$} -- (\intersectX,\intersectY);
  \draw[dashed]  (\QPX,0) node[below] {$Q_2$} -- (\QPX,\QPY);
  \draw[dashed]  (0,\QPY) node[below] {$P_2$} -- (\QPX,\QPY);

  \end{tikzpicture}

\newpage





